Learning to Dispatch: A Reinforcement Learning Framework for Train Dispatch Networks

### 2025-04-22 paper/main.tex
Push so I can work on my mac

\begin{figure}
    \centering
    \begin{tikzpicture}[
        node/.style={draw,text width=2.5cm, align=center,rounded corners, fill=blue!20, minimum width=1.5cm, minimum height=1cm},
        edge/.style={->, thick},
        resource/.style={draw, rounded corners, fill=orange!30, minimum width=1.5cm, minimum height=1cm},
        every node/.style={font=\small}
    ]
        % Nodes
        \node[node] (op0) at (0, 0) {op 0 \\ $\delta = 5$ \\ $r_1$};
        \node[node] (op1) at (3, 1.5) {op 1 \\ $\delta = 0$ \\ $r_1, r_2$};
        \node[node] (op2) at (3, -1.5) {op 2 \\ $\delta = 0$ \\ $r_1, r_3$};
        \node[node] (op3) at (6, 0) {op 3 \\ $\delta = 5$ \\ $r_4$};
        \node[node] (op7) at (9, 0) {op 7 \\ $\delta = 0$ \\ $t \leq 10$};

        % Edges
        \draw[edge] (op0) -- (op1);
        \draw[edge] (op0) -- (op2);
        \draw[edge] (op1) -- (op3);
        \draw[edge] (op2) -- (op3);
        \draw[edge] (op3) -- (op7);
    \end{tikzpicture}
    \caption{Example Train Operation DAG with resource and duration constraints.}
    \label{fig:train_dag}
\end{figure}

@@

\section{Preliminary Agent Results}
\label{sse:results}

\subsection{Deep Graph Q-Network Agent}
\label{sss:agent}

\subsection{Solutions}
\label{sss:solutions}

@@

>>>>

\begin{figure}
    \centering
    \begin{tikzpicture}[
        node/.style={circle, draw, fill=blue!20, minimum size=1.2cm, align=center},
        edge/.style={->, thick},
        resource/.style={draw, rounded corners, fill=orange!30, minimum width=1.5cm, minimum height=1cm},
        every node/.style={font=\small}
    ]
        % Nodes
        \node[node] (op0) at (0, 0) {op 0 \\ $\delta = 5$ \\ $[]$};
        \node[node] (op1) at (3, 1.5) {op 1 \\ $\delta = 0$ \\ $r_2$};
        \node[node] (op2) at (3, -1.5) {op 2 \\ $\delta = 0$ \\ $r_1, r_2$};
        \node[node] (op3) at (6, 0) {op 3 \\ $\delta = 5$ \\ $r_1$};
        \node[node] (op4) at (9, 0) {op 4 \\ $\delta = 0$ \\ $[]$};

        % Edges
        \draw[edge] (op0) -- (op1);
        \draw[edge] (op0) -- (op2);
        \draw[edge] (op1) -- (op3);
        \draw[edge] (op2) -- (op3);
        \draw[edge] (op3) -- (op4);

        % Additional DAG
        \node[node] (op0_new) at (0, -4) {op 0 \\ $\delta = 0$ \\ $[]$};
        \node[node] (op1_new) at (3, -4) {op 1 \\ $\delta = 0$ \\ $r_1$};
        \node[node] (op2_new) at (6, -4) {op 2 \\ $\delta = 0$ \\ $[]$};

        % Edges
        \draw[edge] (op0_new) -- (op1_new);
        \draw[edge] (op1_new) -- (op2_new);

        \draw[<->, red, thick] (op1) -- (op2);
        \draw[<->, red, thick] (op3) -- (op2);
        \draw[<->, red, thick] (op1_new) -- (op2);
        \draw[<->, red, thick] (op1_new) -- (op3);

    \end{tikzpicture}
    \caption{Example Train Operation DAG with resource and duration constraints.}
    \label{fig:train_dag}
\end{figure}

@@

% \section{Preliminary Agent Results}
% \label{sse:results}

% \subsection{Deep Graph Q-Network Agent}
% \label{sss:agent}

% \subsection{Solutions}
% \label{sss:solutions}

@@

\begin{figure}
    \begin{tikzpicture}[>=Stealth, node distance=2cm and 2cm]

        % Styles
        \tikzstyle{op} = [draw, minimum width=1.8cm, minimum height=1.2cm]
        \tikzstyle{circleop} = [op, circle]
        \tikzstyle{redarrow} = [->, red, thick]
        \tikzstyle{blackarrow} = [->, thick]

        % Train A
        \node[op] (a0) {op 0\\$r = [\,]$};
        \node[circleop, above right=of a0] (a1) {op 1\\$r = [\,]$};
        \node[circleop, below right=of a0] (a2) {op 2\\$r = [\,]$};
        \node[circleop, right=of a1] (a3) {op 3\\$r = 1$};
        \node[op, right=of a3] (a4) {op 4\\$r = [\,]$};

        % Arrows for Train A
        \draw[blackarrow] (a0) -- (a1);
        \draw[blackarrow] (a0) -- (a2);
        \draw[blackarrow] (a1) -- (a3);
        \draw[blackarrow] (a3) -- (a4);

        % Red connections (Train A feedback or dependencies)
        \draw[redarrow] (a1) -- (a2);
        \draw[redarrow] (a2) -- (a1);
        \draw[redarrow] (a2) -- (a3);
        \draw[redarrow] (a2) -- (a2);

        % Train B
        \node[op, below left=4cm and 2cm of a2] (b0) {op 0\\$r = [\,]$};
        \node[circleop, right=of b0] (b1) {op 1\\$r = 1$};
        \node[op, right=of b1] (b2) {op 2\\$r = [\,]$};

        % Arrows for Train B
        \draw[blackarrow] (b0) -- (b1);
        \draw[blackarrow] (b1) -- (b2);

        % Labels
        \node[above left=0.5cm of a0] {\textbf{Train A}};
        \node[above left=0.5cm of b0] {\textbf{Train B}};

    \end{tikzpicture}

\end{figure}
